DATA 624 Homework 2

### 2020-02-14 DATA624/HW2.Rmd
More work on HW2

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(fpp2)
```

@@

* `usnetelec`
* `usgdp`
* `mcopper`
* `enplanements`

@@

@@

@@

Split the data into two parts using
```{r}
myts.train <- window(myts, end=c(2010,12))
myts.test <- window(myts, start=2011)
```

@@

```{r}
autoplot(myts) +
  autolayer(myts.train, series="Training") +
  autolayer(myts.test, series="Test")
```

@@

```{r}
accuracy(fc,myts.test)
```

@@

@@

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(fpp2)
library(gridExtra)
library(readxl)
```

@@

**I will answer these questions with side by side visualizations of the data.  The appropriate Box-Cox transformation will be on the right hand side with the lambda in the title.**

```{r}
side_by_side <- function(x, y){
  lambda <- BoxCox.lambda(x)
  plot1 <- autoplot(x) +
    ggtitle("Original") +
    ylab(y) + 
    theme(axis.title.x = element_blank())
  plot2 <- autoplot(BoxCox(x, lambda)) +
    ggtitle(paste0("Box-Cox Transformed (lambda=", round(lambda, 4),")")) +
    theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) 
  grid.arrange(plot1, plot2, ncol = 2)
}
```

### usnetelec

```{r}
side_by_side(usnetelec, "US Net Electricity Generation")
```

### usgdp

```{r}
side_by_side(usgdp, "US GDP")
```

### mcopper

```{r}
side_by_side(mcopper, "Monthly Copper Prices")
```

### enplanements

```{r}
side_by_side(enplanements, "Monthly US Domestic Enplanements")
```

@@

```{r}
side_by_side(cangas, "Monthly Canadian Gas Production")
```

**The Box-Cox transformation does not help with this timeseries because the variation is initially small, then gets large, then gets small again.  Box-Cox was not designed to handle this case.  It was designed for cases where the variance increases or decreases over time.**

@@

```{r}
retaildata <- read_excel("retail.xlsx", skip = 1)
myts <- ts(retaildata[, "A3349873A"], frequency = 12, start = c(1982, 4))
side_by_side(myts, "Retail Sales")
```

**The variation was increasing over time in the original data.  It has become significantly more uniform once it is transformed with a lambda of 0.13.  Because the variance was increasing over time this was an effective transformation.**

@@

Split the data into two parts using
```{r}
myts.train <- window(myts, end = c(2010, 12))
myts.test <- window(myts, start = 2011)
```

@@

```{r}
autoplot(myts) +
  autolayer(myts.train, series = "Training") +
  autolayer(myts.test, series = "Test")
```

@@

```{r}
accuracy(fc, myts.test)
```

@@

**They do appear to be normally distributed however with a sligh positve skew.  The residuals do no appear to be uncorrelated.  The Ljung-Box test has a p value that is less than 0.05.  This suggests there is more information that can be discovered and that the seasonal naive model is not the best model.**

@@

**The accuracy measures are quite sensitive to the training/test split. The values are significantly different between the two.  This would suggest that the model does not generalize well.**
